\LARGE \bf\vspace{-10mm} Face Recognition: Too Bias, or Not Too Bias?

### 2020-02-01 todo.tex
Initial Overleaf Import

\begingroup
\let\clearpage\relax 
\onecolumn 
\newpage

@@

    \end{itemize}
    \end{itemize}
\end{enumerate}
\subsection{Samson}
\begin{enumerate}
    \item Sanity test with mxnet (Samson),  26 Friday 2019
    \item Patrick at NIST (Samson: Tomorrow set a time)
    \item Run repeat test with mx-net version of ArcFace (resnet 100)
    \item Reach out to IBM, for Diversity in Faces
    \item Work with Joe to determine goals for data, i.e., specifications of what we would like to include and means of obtaining more if needed.
\end{enumerate}
\subsection{Gena}
\begin{enumerate}
    \item TBD
\end{enumerate}

@@

\begin{figure}[h]
\setlength{\unitlength}{0.14in} % selecting unit length
\centering % used for centering Figure
\begin{picture}(32,15) % picture environment with the size (dimensions)
 % 32 length units wide, and 15 units high.
\put(3,4){\framebox(6,3){$H_{B}(q)$}}
\put(13,4){\framebox(6,3){$N[\cdot]$}}
\put(23,4){\framebox(6,3){$H_{C}(q)$}}
\put(0,5.5){\vector(1,0){3}}\put(9,5.5){\vector(1,0){4}}
\put(19,5.5){\vector(1,0){4}}\put(29,5.5){\vector(1,0){3}}
\put(-1,6.5) {$u(k)$}\put(30,6.5) {$y(k)$} \put(9.5,6.5)
{$x_{B}(k)$}\put(19.5,6.5) {$x_{C}(k)$}
\end{picture}
\caption{An LNL Block Oriented Model Structure} % title of the Figure
\label{fig:lnlblock} % label to refer figure in text
\end{figure}

@@

\endgroup

>>>>

\begingroup
\let\clearpage\relax 
\onecolumn 
\newpage
\newpage\newpage

@@

    \end{itemize}
    \end{itemize}
\end{enumerate}
\subsection{Samson}
\begin{enumerate}
    \item Sanity test with mxnet (Samson),  26 Friday 2019
    \item Patrick at NIST (Samson: Tomorrow set a time)
    \item Run repeat test with mx-net version of ArcFace (resnet 100)
    \item Reach out to IBM, for Diversity in Faces
    \item Work with Joe (and Gena if applicable, Nikil also if so) to determine goals for data, i.e., specifications of what we would like to include and means of obtaining more if needed.

\end{enumerate}
\subsection{Gena}
\begin{enumerate}
    \item Arrange to have quick powwow to get caught up with project, understand and help refine/improve goals and themes for this research track/ paper. Also, speak on what type of role you would like to play/ action items if any.
\end{enumerate}

@@

% \begin{figure}[h]
% \setlength{\unitlength}{0.14in} % selecting unit length
% \centering % used for centering Figure
% \begin{picture}(32,15) % picture environment with the size (dimensions)
%  % 32 length units wide, and 15 units high.
% \put(3,4){\framebox(6,3){$H_{B}(q)$}}
% \put(13,4){\framebox(6,3){$N[\cdot]$}}
% \put(23,4){\framebox(6,3){$H_{C}(q)$}}
% \put(0,5.5){\vector(1,0){3}}\put(9,5.5){\vector(1,0){4}}
% \put(19,5.5){\vector(1,0){4}}\put(29,5.5){\vector(1,0){3}}
% \put(-1,6.5) {$u(k)$}\put(30,6.5) {$y(k)$} \put(9.5,6.5)
% {$x_{B}(k)$}\put(19.5,6.5) {$x_{C}(k)$}
% \end{picture}
% \caption{An LNL Block Oriented Model Structure} % title of the Figure
% \label{fig:lnlblock} % label to refer figure in text
% \end{figure}

@@

\endgroup
\twocolumn
